The Lipid Interactome Repository

### 2025-01-22 MaintenanceInstructions.qmd
adding hover functionality to structures is hard...

Under the "IndividualStudies" folder are the .qmd files that define the preparation of each corresponding .html page. The data going into these .qmd files is stored under the "DataTables" subfolder.

@@

Any changes can then be pushed to the github repository; Netlify will pull the changes and automatically deploy the updated site! See site owners for Netlify login information and .git access. It will be TBD how GitHub ownership is transferred after I leave.

@@

If your data looks at all like [Alix's](https://lipidinteractomicsrepository.netlify.app/individualstudies/at_2025){target="_blank"} or [Scotty's](https://lipidinteractomicsrepository.netlify.app/individualstudies/sf_2024){target="_blank"}, the ggplot functions I built in the ggplot_styles.R file will apply. Call the RankedOrderPlotStandard() and VolcanoPlotStandardized() functions to produce these plots with the same standardized formatting. On that note, you can alter the ggplot_styles.R file to change the standardized formatting.

>>>>

Under the "IndividualStudies" folder are the .qmd files that define the preparation of each corresponding .html page. The data going into these .qmd files is stored under the "DataTables" subfolder. Under the "LipidProbe" folder are the .qmd files that define the pages on each individual probe. Much of the information is copied between the two sets of pages, so be careful when making changes to one, as corresponding changes should be made elsewhere!

@@

### GitHub repository

After changes are made to the .qmd files and then rendered, the changes can then be pushed to the GitHub repository: <git@github.com:gaelenDG/LipidInteractomics_Website.git>. Netlify will pull the changes and automatically deploy the updated site! See site owners for Netlify login information and .git access.

Cloning the GitHub repository should be sufficient for gaining access to all of the files in this website - though collaborators will need to be added manually by Gaelen, the repository administrator. More details will go here once a more formal pull request workflow is in place!

@@

If your data looks at all like [Alix's](https://lipidinteractomicsrepository.netlify.app/individualstudies/at_2025){target="_blank"} or [Scotty's](https://lipidinteractomicsrepository.netlify.app/individualstudies/sf_2024){target="_blank"}, the ggplot functions I built in the ggplot_styles.R file will apply. Call the RankedOrderPlotStandard(), VolcanoPlotStandardized(), and MAStandard() functions to produce these plots with the same standardized formatting. On that note, you can alter the ggplot_styles.R file to change the standardized formatting.

### 2025-01-22 TrifunctionalLipidProbesOverview.qmd
Updates after weekly meeting
adding hover functionality to structures is hard...

---
title: "Multifunctional Lipid Probes Primer"
author: "Gaelen Guzman"
format: 
  html:
    embed-resources: false
standalone: true
---

I could use help writing a succinct article here to describe the use of these probes. We can additionally reference prior publications here -- but I think it would be nice to have a novel description with figures for this site.

I have a few example figures, but I am open to using whichever figures seem best -- if that is a new figure, I'll need guidance on what it should look like.

@@

:::{.border}
![](/LipidProbe/Structures/SphingosineStructure.png){group="ProbePrimer"}
:::

>>>>

---
title: "Multifunctional Lipid Probes Background"
author: "Gaelen Guzman"
format: 
  html:
    embed-resources: false
standalone: true
---

Functionalized lipid probes are at the intersection of several niche biotechnologies. This overview will serve as a brief summary of the capabilities, nuances, and caveats of their utility. Additional resources and published review articles will be linked below for greater detail.

@@

:::{.border}

```{r setup, echo=FALSE, include=FALSE}
library(plotly)

library(plotly)

# Load your image
image_url <- "LipidProbe/Structures/SphingosineStructure.png"

# Define hover regions (as rectangles)
shapes <- list(
  list(type = "rect", x0 = 0, x1 = 32, y0 = 50, y1 = 85,
       line = list(color = "red", width = 2),
       fillcolor = "rgba(255, 0, 0, 0.1)",  # Transparent fill
       name = "Region 1", hoverinfo = "none"),
  list(type = "rect", x0 = 50, x1 = 70, y0 = 40, y1 = 60,
       line = list(color = "blue", width = 2),
       fillcolor = "rgba(0, 0, 255, 0.1)",  # Transparent fill
       name = "Region 2", hoverinfo = "none")
)

# Define hover annotations
hover_annotations <- data.frame(
  x = c(20, 60),  # Midpoints of rectangles
  y = c(80, 50),
  text = c("Region 1 Info", "Region 2 Info")
)

# Create the plot
plot <- plot_ly() %>%
  add_trace(
    data = hover_annotations,
    x = ~x, y = ~y, text = ~text,
    mode = "markers",
    marker = list(opacity = 0),  # Invisible markers
    hoverinfo = "text"  # Show hover text
  ) %>%
  layout(
    shapes = shapes,
    images = list(
      list(
        source = image_url,
        xref = "x",
        yref = "y",
        x = 0,
        y = 100,
        sizex = 100,
        sizey = 100,
        xanchor = "left",
        yanchor = "top",
        layer = "below"
      )
    ),
    xaxis = list(visible = FALSE, range = c(0, 100)),
    yaxis = list(visible = FALSE, range = c(0, 100))
  )
```

```{r, echo=FALSE, warnings=FALSE}
# Render the plot
plot

```
:::

:::{.border}
```{=html}
<div style="position: relative; display: inline-block;">
  <img src="LipidProbe/Structures/SphingosineStructure.png" alt="Interactive Image" style="width: 500px;">

  <!-- Popup 1 -->
  <div style="position: absolute; top: 20%; left: 10%; cursor: pointer;">
    <span class="popup-hover" title="Popup for Point 1">🔴</span>
  </div>

  <!-- Popup 2 -->
  <div style="position: absolute; top: 70%; left: 50%; cursor: pointer;">
    <span class="popup-hover" title="Popup for Point 2">🔵</span>
  </div>

  <!-- Hover region 1 -->
  <div style="position: absolute; top: 20%; left: 10%; width: 15%; height: 15%; border: 2px solid red; box-sizing: border-box;"
       title="Region 1 Info"></div>

  <!-- Hover region 2 -->
  <div style="position: absolute; top: 50%; left: 50%; width: 20%; height: 20%; border: 2px solid blue; box-sizing: border-box;"
       title="Region 2 Info"></div>
</div>
</div>

<style>
  .popup-hover:hover::after {
    content: attr(title);
    position: absolute;
    top: -30px;
    left: 0;
    background: white;
    color: black;
    padding: 5px;
    border: 1px solid #ccc;
    border-radius: 5px;
    white-space: nowrap;
    box-shadow: 0px 4px 6px rgba(0, 0, 0, 0.1);
  }
</style>

```

:::

### 2025-01-22 index.qmd
adding hover functionality to structures is hard...

A blurb about the objective of this site, maybe a gallery of images from select publications to put here.

>>>>

The goal of this site is to increase the accessibility of proteomics data utilizing multi-functionalized lipid analogs/probes to identify the lipid::protein interactions of biologically active lipids.

Explore the lipids below to see their published interactomes.

See our [Functional Lipid Probes Overview](/TrifunctionalLipidProbesOverview.qmd) for more details about how these lipid analogs are used.
